More than one Author with different Affiliations

### 2016-02-19 NatPlant2/manuscript.tex
working late with coffee
a few updates

\documentclass[12pt,a4paper]{article}
\usepackage{cite}
\usepackage{color}
\usepackage{pgf}
\usepackage[margin=1in]{geometry}
%\usepackage{hyperref}
\usepackage[normalem]{ulem}
\newcommand{\jri}[1]{\textcolor{red}{\scriptsize #1}}
\newcommand{\mbh}[1]{\textcolor{blue}{\scriptsize #1}}
\newcommand{\tmb}[1]{\textcolor{brown}{\scriptsize #1}}
\newcommand{\citex}{\textcolor{red}{\bf CITE}}
\newcommand{\X}{\textcolor{red}{\bf X}}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[colorlinks=true,
            linkcolor=red,
            urlcolor=blue,
            citecolor=gray]{hyperref}
\usepackage{natbib}
\bibpunct{}{}{,}{s}{}{\textsuperscript{,}}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\maketitle

@@

\subsection*{Demography of maize domestication} %JRI
We next estimated a demographic model of maize domestication (Figure \ref{fig:bottleneck}). 
To minimize the impact of selection on our estimates \jri{cite http://onlinelibrary.wiley.com/doi/10.1111/mec.13390/full}, we only included sites \textgreater 5kb from genes.  
The most likely model estimates an ancestral population mutation rate of $\theta=0.0147$ per bp, which translates to an effective population size of $N_a \approx 123,000$ teosinte individuals.
We estimate that maize split from teosinte $\approx 15,000$ generations in the past, with an initial size of only $\approx 5\% $ of the ancestral $N_a$. 
After its split from teosinte, our model posits exponential population growth in maize, estimating a final modern effective population size of $N_m \approx 370,000$.
Maize and teosinte have continued to exchange migrants after the population split, with gene flow between the populations estimated at $M_{tm} =  1.1 \times 10^{-5} \times N_a $  migrants per generation from teosinte to maize and $M_{mt} =  1.4 \times 10^{-5} \times N_a$ migrants from maize to teosinte.

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{cite}
\usepackage{color}
\usepackage{pgf}
\usepackage[margin=1in]{geometry}
%\usepackage{hyperref}
\usepackage[normalem]{ulem}
%\usepackage{coffee4}
\newcommand{\jri}[1]{\textcolor{red}{\scriptsize #1}}
\newcommand{\mbh}[1]{\textcolor{blue}{\scriptsize #1}}
\newcommand{\tmb}[1]{\textcolor{brown}{\scriptsize #1}}
\newcommand{\citex}{\textcolor{red}{\bf CITE}}
\newcommand{\X}{\textcolor{red}{\bf X}}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[colorlinks=true,
            linkcolor=red,
            urlcolor=blue,
            citecolor=gray]{hyperref}
\usepackage{natbib}
\bibpunct{}{}{,}{s}{}{\textsuperscript{,}}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\maketitle
%\cofeAm{1}{1.0}{0}{5.5cm}{3cm}

@@

\subsection*{Demography of maize domestication} %JRI
We next estimated a demographic model of maize domestication (Figure \ref{fig:bottleneck}). 
To minimize the impact of selection on our estimates \jri{cite http://onlinelibrary.wiley.com/doi/10.1111/mec.13390/full}, we only included sites \textgreater 5kb from genes.  
The most likely model estimates an ancestral population mutation rate of $\theta=0.0147$ per bp, which translates to an effective population size of $N_a \approx 123,000$ teosinte individuals.
We estimate that maize split from teosinte $\approx 15,000$ generations in the past, with an initial size of only $\approx 5\% $ of the ancestral $N_a$. 
After its split from teosinte, our model posits exponential population growth in maize, estimating a final modern effective population size of $N_m \approx 370,000$.
Although, our model provides only a rough approximation of migration rates, we included migration parameters during demographic inference because omitting these could bias our population size estimates. Still, we observe that maize and teosinte have continued to exchange migrants after the population split. We estimate that gene flow from teosinte to maize was $M_{tm} =  1.1 \times 10^{-5} \times N_a $  migrants per generation, and from maize to teosinte we estimate $M_{mt} =  1.4 \times 10^{-5} \times N_a$ migrants per generation.
